### 2015-12-03 paper.tex
Change to past tense
Test matrix section names and descriptions are now in the exp repo README; resolves #21

Data collection runs were separated into individual tows, for which all
independent variables---tow speed, tip speed ratio, velocity probe
position---were held constant. These runs were grouped into logical test matrix
``sections,'' in which typically a single independent variable was varied. Test
matrix section names and descriptions are given below, which outline the
experimental data and code repository \cite{Bachant2015-RM2-data}.

\textbf{\textit{[The list below is too detailed for a journal paper - suggest to remove the list and leave only the citation]}}
\begin{itemize}

    \item \texttt{Perf-\{speed\}}: Performance curve at \texttt{\{speed\}} m/s
    tow speed, performed for (0.4, 0.6, 0.8, 1.0, 1.2) m/s.

    \item \texttt{Perf-\{speed\}-b}: Second performance curve at
    \texttt{\{speed\}} m/s, performed for the same tow speeds as above for
    reduced statistical uncertainty.

    \item \texttt{Perf-1.0-covers}: Performance curve at 1.0 m/s tow speed with
    cylindrical strut covers.

    \item \texttt{Perf-1.0-no-blades-covers}: Performance curve at 1.0 m/s with
    no blades and cylindrical strut covers.

    \item \texttt{Perf-1.0-no-blades}: Performance curve at 1.0 m/s with no
    blades (NACA 0021 struts only).

    \item \texttt{Perf-tsr\_0}: Performance at $\lambda=3.1$ for multiple tow
    speeds.

    \item \texttt{Perf-tsr\_0-b}: Additional set of runs duplicating the
    \texttt{Perf-tsr\_0} parameters.

    \item \texttt{Strut-torque-covers}: Measuring parasitic torque from
    cylindrical struts without towing.

    \item \texttt{Strut-torque}: Measuring parasitic torque from
    NACA 0021 struts without towing.

    \item \texttt{Tare-drag}: Drag on the turbine frame measured with the turbine
    removed.

    \item \texttt{Tare-torque}: Measurements of friction torque in shaft
    bearings for a range of RPMs used in the experiments.

    \item \texttt{Wake-\{speed\}-\{z/H\}}: Cross-stream wake profile at 1 m
    downstream ($x/D=0.93$), $\lambda=3.1$, \texttt{\{speed\}} m/s tow speed,
    and \texttt{\{z/H\}} vertical location.
\end{itemize}

@@

Selecting $t_{95}$ requires an estimate for degrees of freedom $\nu_X$, which can
be obtained using the Welch--Satterthwaite formula
\begin{equation}
    \nu_X = \frac{\left(s_X^2 + \sum_{k=1}^M b_k^2 \right)^2} {s_X^4/\nu_{s_X} +
        \sum_{k=1}^M b_k^4/\nu_{b_k}},
\end{equation}
where $\nu_{s_X}$ is the number of degrees of freedom associated with $s_X$ and
$\nu_{b_k}$ is the number of degrees of freedom associated with $b_k$.
$\nu_{s_X}$ is assumed to be $(N-1)$, where $N$ is the number of independent
samples (or turbine revolutions). $\nu_{b_k}$ will be estimated as
\begin{equation}
    \nu_{b_k} = \frac{1}{2} \left( \frac{\Delta b_k}{b_k} \right)^{-2},
\end{equation}
where the quantity in parentheses is the relative uncertainty of $b_k$.

>>>>

Data collection runs were separated into individual tows, for which all
independent variables---tow speed, tip speed ratio, velocity probe
position---were held constant. These runs were grouped into logical test matrix
``sections,'' in which typically a single independent variable was varied. Test
matrix section names and descriptions are provided in the \texttt{README.md}
file of the experimental data and code repository \cite{Bachant2015-RM2-data}.

@@

Selecting $t_{95}$ requires an estimate for degrees of freedom $\nu_X$, which
was obtained using the Welch--Satterthwaite formula
\begin{equation}
    \nu_X = \frac{\left(s_X^2 + \sum_{k=1}^M b_k^2 \right)^2} {s_X^4/\nu_{s_X} +
        \sum_{k=1}^M b_k^4/\nu_{b_k}},
\end{equation}
where $\nu_{s_X}$ is the number of degrees of freedom associated with $s_X$ and
$\nu_{b_k}$ is the number of degrees of freedom associated with $b_k$.
$\nu_{s_X}$ is assumed to be $(N-1)$, where $N$ is the number of independent
samples (or turbine revolutions). $\nu_{b_k}$ will be estimated as
\begin{equation}
    \nu_{b_k} = \frac{1}{2} \left( \frac{\Delta b_k}{b_k} \right)^{-2},
\end{equation}
where the quantity in parentheses is the relative uncertainty of $b_k$.
